Automated segmentation and description of the internal morphology of human permanent teeth by means of micro-CT

### 2021-04-13 manuscript.tex
Link to published version [ci skip]
This build is based on
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/a58577793380052c7fdf515ff2a5360b9e525391.

This commit was created by the following CI build and job:
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/a58577793380052c7fdf515ff2a5360b9e525391/checks
https://github.com/habi/zmk-tooth-cohort-method-manuscript/runs/744884877

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...bc06c5bf415aa5a3bda760e9c9617cd213d52015}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/bc06c5bf415aa5a3bda760e9c9617cd213d52015/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/bc06c5bf415aa5a3bda760e9c9617cd213d52015}{habi/zmk-tooth-cohort-method-manuscript@bc06c5b}
on April 9, 2021.

@@

\leavevmode\hypertarget{ref-10OKzEtEb}{}%
37. Fedlex. \url{https://www.fedlex.admin.ch/eli/cc/2013/617/en}. Accessed 9 Apr 2021.
\end{cslreferences}

>>>>

A published version of this manuscript is available at \url{https://doi.org/10.1186/s12903-021-01551-x}.
This current version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/6d0a6402c44cb9745875171d2d33c37b4d7fe4be...a58577793380052c7fdf515ff2a5360b9e525391}{has been updated} with minor corrections compared to the submitted version.
These errors have been corrected in the proof-stage at BMC Oral Health and are \emph{not} present in the published version.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/a58577793380052c7fdf515ff2a5360b9e525391/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/a58577793380052c7fdf515ff2a5360b9e525391}{habi/zmk-tooth-cohort-method-manuscript@a585777}
on April 13, 2021.

@@

\leavevmode\hypertarget{ref-10OKzEtEb}{}%
37. Fedlex. \url{https://www.fedlex.admin.ch/eli/cc/2013/617/en}. Accessed 13 Apr 2021.
\end{cslreferences}
